---
title: "Homework Week 47"
author: "Asger Kammer Pedersen"
date: " 2021/11/30"
output: 
  html_document:
      toc: TRUE
      toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
library(tidyverse)
```



```{r data}
Western_Europe <- read_csv("Data/homicide-rates-across-western-europe.csv")
```



```{r}
names(Western_Europe)[1] <- 'Country'
```

# Homework Week 47

```{r }
ggplot(data = Western_Europe) + 
  geom_smooth(mapping = aes(x = Year, 
                           y = Western_Europe$Homicide_per_100k, 
                           color = Country)) +
  labs(x = "Year",
       y = "Number of Homicides per 100,000 people",
       title = "Homicide rate in Europe from 1300-2000")

```


```{r }
ggplot(data = Western_Europe) + 
  geom_line(mapping = aes(x = Year, 
                           y = Western_Europe$Homicide_per_100k, 
                           color = Country)) +
  facet_wrap(~ Country, nrow = 3,ncol = 2) +
  labs(x = "Year",
       y = "Homicides per 100,000",
       title = "Homicide rate in Western Europe from 1300-2000")
theme(legend.position = "bottom")
```

```{r}

kings <- read_csv("./Data/Exerxice-1-Ark1.csv")
kings$Duration <- kings$End_of_Reign-kings$Beginning_of_Reign
kings[30,1:6]
kings1 <- kings[-c(30,40),]

mean(kings1$Duration,na.rm=T)
class(kings1$Duration)


kings1 <- kings1 %>% 
  mutate(midyear = Beginning_of_Reign -(Beginning_of_Reign-End_of_Reign)/2)
```





```{r}
# YOUR CODE HERE:
ggplot(kings1, aes(x=midyear,y=Duration))+
  geom_point()+
  geom_smooth()+
  labs(title = "Duration avg. of rule for danish kigns",
       x="Mid-Year",y="Duration")+
  theme_bw()+
  theme(text = element_text(size=16))
```


**Your Tasks:**
## Task 1
1) the column name Western_Europe$`Homicide rate in Europe over long-term (per 100,000) is not very easy to work with. Relabel it to 'homicides_per_100k' inside R after loading the dataset and then edit all the ggplots.

 As shown above in the gg_plots 

## Task 2
2) The basic plot and following facet-plot (combination plot) is great, but geom_point - a scatterplot - is not the best choice for showing long-term data. Can you change both plots to more suitable type of rendering? 

I have chosen geom_smooth and geom_line as possible ways to show render long term data. 

## Task 3
3) Can you change the facet "layout" to two columns and three rows so that the trends are easier to see? 

Add "ncol = 2" after nrow in the facets 

## Task 4
4) Move the legend from the current position on the side to below the facets, and label it "Country" instead of "Entity".

Renaming to "Country" instead of "Entity":

names(Western_Europe)[1] <- 'Country' 

Then I renamed the places which had Entity in the plots to Country

I used this code to get the legend to go at the bottom:
theme(legend.direction = "bottom")
as was instructed to me by fellow students, but it does not seem to have the desired function. I do not know why it does not work.

## Task 5
5) Add a floating table of contents to your Rmarkdown document, provide informative chunk-names to all your R chunks, and automatically generate a timestamp to show when the document was last updated. (Hint: check the Rmarkdown episode in our Data Carpentry tutorial)

I changed my header to be as follows: 
title: "Homework Week 47"
author: "Asger Kammer Pedersen"
date: " 2021/11/30"
output: 
  html_document:
      toc: TRUE
      toc_float: TRUE

## Task 6
6) Fill in the empty code chunk with a ggplot of your Danish kings: loading the data, calculating the mid-year, and plotting the duration of reign (y axis) over the mid-year  (x axis), using geom_smooth()

The code for how i created it is as follows: 

kings <- read_csv("./Data/Exerxice-1-Ark1.csv")
kings$Duration <- kings$End_of_Reign-kings$Beginning_of_Reign
kings[30,1:6]
kings1 <- kings[-c(30,40),]

mean(kings1$Duration,na.rm=T)
class(kings1$Duration)


kings1 <- kings1 %>% 
  mutate(midyear = Beginning_of_Reign -(Beginning_of_Reign-End_of_Reign)/2)
  
I did this so I would have both midyear and duration in my .csv file

ggplot(kings1, aes(x=midyear,y=Duration))+
  geom_point()+
  geom_smooth()+
  labs(title = "Duration avg. of rule for danish kigns",
       x="Mid-Year",y="Duration")+
  theme_bw()+
  theme(text = element_text(size=16))
  
Then i did this to create a ggplot with the desired data.
I took added in geom_point extra accesibility. 

## Task7
7) Comment briefly what is your opinion on the basis of the data visualisations: are we more civilized today?
If we only base our level of civilization on homicide rates, then I would say yes, but it is an over all pretty hollow argument. What I am saying is that there has to be more to it than that. 